%ADD HOBBIESSSSSSSSSS
%GitHub


\documentclass[]{farzad-resume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\tiny }

\namesection{Zad}{Vakili}{
\href{mailto:vakilif@mcmaster.ca}
{vakilif@mcmaster.ca} | (647)834-6900 | https://github.com/f1377v
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.30\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\subsection{McMaster University}
\descript{Software engineering Co-op, Minor in innovations}
\location{ Hamilton, ON} Expected Graduation 2021 
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Links}
%LinkedIn://  \href{https://www.linkedin.com/in/danielrazavi}{\custombold{danielrazavi}} \\
%Github:// \href{https://github.com/DanielRazavi}{\custombold{DanielRazavi}}\\
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}

Dean Honor Award \\
Mcmaster President Entrance Award, \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Python \textbullet{} Java \textbullet{} C\# \textbullet {}  HTML\textbullet{} CSS \\ 
\LaTeX\ \textbullet{} ELM\\
\sectionsep

\subsection{Technologies}
Git \textbullet{} Google Cloud Platform \textbullet{} Ubuntu  \textbullet{} Microsoft Azure \textbullet{} Windows
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work experience}
%\subsection{Personal Website}
%\vspace{\topsep}
%\begin{tightemize}\item Made a personal website that is used to furthur showcase
%\ my projects to visiters and potential emplyers. Used Sass and Jade to create content and style the site, while employing the use of Gulp to automate tasks. Used Jekyll as the CMS for the projects sections. (Work in progress)
%\end{tightemize}
%\sectionsep
\runsubsection{Software Developer}
\descript{| from July 2020 to November 2020 }
\location{Adlib Software | Burlington, ON}
\vspace{\topsep}
\begin{tightemize}
    \item {\fontsize{10.5}{12.6} \selectfont Performed a variety of tasks from testing to developing with minimal supervision which required me to grow strong communication, interpersonal and debugging skills.
	\item Integrated new serialization approach (Google Protocol Buffers) instead of json serilization, increasing time and memory efficiency while supporting the existing code in two distributed systems.
	\item Worked with C\# and Python.
	\item Being in an agile environment required me to familiarize myself with version control (Microsoft Azure in specific) and it's best practices.
	\item Being in an agile environment required me to follow coding practices such as test driven development and pair programming.}
\end{tightemize}
\sectionsep

\runsubsection{Programming Instructor}
\descript{| from Sept 2018 to Sept 2019 }
\location{Mcmaster University | Hamilton, ON}
\vspace{\topsep}
\vspace{\topsep}
\begin{tightemize}
  \item Created a math game from scratch with ELM functional language to help students with their studies and make them more interested in programming.
  \item Taught programming to 150+ students at two different schools in collaboration with other software engineering students, through which my communication and team work skills enhanced significantly.
  \item Assisted with designing an elaborate lesson plan for students.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section {projects \fontsize{9}{10.8} \selectfont (Check github link at the top)}

\runsubsection{Decoration Company Website}
\vspace{\topsep}
\begin{tightemize}
    \item {\fontsize{10.5}{12.6} \selectfont Created a website with python for a decoration company.(https://amir-nl.appspot.com/)
    \item The website has a database which was implemented using flask-SQLalchemy, as well as a full-text search among the items saved within the database.It also features a secure login system.
    \item Developed a standard reactive front end from scratch, using HTML ,CSS and java script.}
\end{tightemize}
\sectionsep

\runsubsection{Celest Game}
\vspace{\topsep}
\begin{tightemize}
    \item {\fontsize{10.5}{12.6} \selectfont A joint project with other software engineering students in which we went through the whole process of requirements engineering and Created a thorough documetation containing MIS (Module Interface Specification), test plan and development plan.
	\item The game has a presentation-abstraction-control (PAC) architectureis, created using c\# and Unity game engine.}
\end{tightemize}
\sectionsep

\runsubsection{Math game}
\vspace{\topsep}
\begin{tightemize}
    \item {\fontsize{10.5}{12.6} \selectfont Created a mini-game with ELM, a functional language that has a model-view-controller architecture, which is a good choice for making interactive programs like games. 
    \item Built a thorough design by creating local functions and then assembling them together to fulfill the principle of seperation of concerns.
     \item Learned and used multiple graphics library to make the game visually appealing.}

\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACTIVITIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\iffalse
\runsubsection{ALDO GROUP}
\descript{| Sales Associate }
\location{July 2016 – August 2017 | Newmarket, ON}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Cashier and Customer Care at Aldo, Upper Canada Mall.
  Providing excellent customer service to the customers. Learning and adapting
  in short period of time due to constant change in sales. Promoting new products
   and promotional sales.
\end{tightemize}
\fi





\end{minipage}
\end{document}
