%ADD HOBBIESSSSSSSSSS
%GitHub


\documentclass[]{farzad-resume}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\tiny }

\namesection{Farzad}{Vakili}{ |
\href{mailto:f1377v@gmail.com}
{f1377v@gmail.com} | (647)834-6900 }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     ROW ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ROW ONE COLUMN ONE EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}
\section{Education}
\subsection{McMaster University}
\descript{B.S. Software Engineering and Co-op}
%\location{ }
%\sectionsep
\end{minipage}
\hfill
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    ROW ONE COLUMN TWO AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.66\textwidth}
\section{Awards}

Dean Honor Award \\
Mcmaster President Entrance Award \\
%\sectionsep
\end{minipage}
\hfill
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ROW TWO SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{minipage}
\begin{minipage}[t]{\textwidth}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ROW TWO COLUMN ONE LANGAUGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.33\textwidth}
\section{Skills}
\subsection{Languages}
C\# \textbullet{}  Python \textbullet{} SQL \textbullet {}  HTML\textbullet{} CSS \\ 
Javascript \textbullet{} PHP \textbullet{} \LaTeX\
%\sectionsep
\end{minipage}
\begin{minipage}[t]{0.33\textwidth}
\section{}
\subsection{Tools \& Platfroms}
Git \textbullet{}  MySQL \textbullet{} Docker \textbullet{} {\Large .}NET\\
Flask\textbullet{} AWS \textbullet{} Windows Forms\\
Jira
%\sectionsep
\end{minipage}
\begin{minipage}[t]{0.33\textwidth}
\section{}
\subsection{Design}
MVC Architecture \\ 
Object-Oriented Desing \\
Microservices Architecture \\ 
REST API/Services\\
\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Row 3
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\begin{minipage}[t]{\textwidth}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work experience}

\runsubsection{Technical Program Manager}
\descript{| from May 2022 to Jan 2024 }
\location{AMD | Remote}
\vspace{\topsep}
\begin{tightemize}
    {\fontsize{8}{10.4} \selectfont 
	\item Coordinated cross-functional teams consiting of software product managers, software marketing managers, and developers to ensure effective collaboration and communication throughout the lifecycle.
	\item Developed a full stack application that automated task extraction via Jira's REST APIs, generated dynamic Gantt charts, and facilitated real-time project adjustments for enhanced tracking and stakeholder engagement.
	\item  Automated a solution to detect and catalog lifecycle discrepancies at various stages of the development process. Streamlined project oversight by ensuring that key checkpoints were flagged for review, enhancing efficiency and reducing project delays. }
\end{tightemize}

\begin{skillsection}
{\custombolder{Skills:} C\# \textbullet{} REST APIs \textbullet{} JavaScript \textbullet{} HTML5 \textbullet{} CSS3 \textbullet{} Git \textbullet{} User Interface Design \textbullet{} Model-View-Controller (MVC) \textbullet{} Written/Verbal Communication}
\end{skillsection}

\sectionsep

\runsubsection{Software Developer Intern}
\descript{| from Jan 2021 to August 2021 }
\location{SQI Diagnostics | Toronto, ON}
\vspace{\topsep}
\begin{tightemize}
{\fontsize{8}{10.4} \selectfont 
\item Identified and resolved critical software-to-hardware communication bugs in Hamilton robots performing Covid-19 Antibody Testing. Improving system diagnostics by implementing comprehensive event logging, including detailed time stamps and thread information, enabling faster issue identification and resolution.

\item Full stack development of a custom Windows update manager application, providing users enhanced
control over delaying, executing, or blocking Windows updates, surpassing the flexibility native to
the operating system. Overcoming significant compatibility challenges posed by evolving Windows 10 security protocols.

\item Developed and deployed multiple installer executables utilizing Windows Forms and Windows Presentation Foundation (WPF) for various internal applications. Leveraging .NET framework and advanced UI design to optimize installation experiences .}
\end{tightemize}

\begin{skillsection}
{\custombolder{Skills:} C\# \textbullet{} Object Oriented Programming (OOP) \textbullet{} WinForms \textbullet{} Windows Presentation Foundation (WPF) \textbullet{} .NET Framework \textbullet{} Git \textbullet{} Software Diagnostics}
\end{skillsection}

\sectionsep


\runsubsection{Software Engineer Intern}
\descript{| from May 2020 to December 2020 }
\location{Adlib Software | Burlington, ON}
\vspace{\topsep}
\begin{tightemize}
    {\fontsize{8}{10.4} \selectfont 
	\item Performed a wide array of tasks, including debugging, feature development, and software testing, showcasing strong problem-solving abilities.
	\item Successfully implemented Google Protocol Buffers for data serialization, replacing JSON to improve both memory usage and processing efficiency. Achieving significant performance optimization across two distributed systems, ensuring seamless backward compatibility with existing codebases.
	\item Operated within an Agile framework, actively participating in Test-Driven Development (TDD) and pair programming to ensure high-quality, maintainable code.
	\item Demonstrated a high level of autonomy and proactive ownership over project responsibilities, with minimal oversight required.}
\end{tightemize}

\begin{skillsection}
%{\fontsize{8}{10.4} \selectfont {\color[HTML]{FF0000} Skills}: Python \textbullet{} CI/CD \textbullet{} Microservices}
{\custombolder{Skills:} Python \textbullet{} CI/CD \textbullet{} Microservices \textbullet{} RabbitMQ  \textbullet{} Azure DevOps \textbullet{} Serialization/Deserialization}

\end{skillsection}


\sectionsep

\runsubsection{Programming Instructor}
\descript{| from Sept 2018 to Sept 2019 }
\location{Mcmaster University | Hamilton, ON}
\vspace{\topsep}
\begin{tightemize}
	{\fontsize{8}{10.4} \selectfont
	\item Instructed over 50 students in the ELM functional programming language across two different schools, under the supervision of Dr. Anand and in collaboration with fellow software engineering students.

 	\item Developed an educational math game from scratch using the ELM functional programming language, adhering to user-centered design principles and following Model-View-Controller (MVC) design pattern.}
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACTIVITIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section {project \& courses \fontsize{9}{10.8} \selectfont}

\runsubsection{ Web Systems and Web Computing}
\vspace{\topsep}
\begin{tightemize}
{\fontsize{8}{10.4} \selectfont 
	\item Project-based course involving \textbf{server-side programming:} databases, dynamic languages; \textbf{ client-side programming:} markup, styles, scripts, design, mobile/desktop.
	\item Developed a full stack website with a responsive design for seamless usability across devices of all sizes, ensuring cross-browser compatibility on popular browser. Deployed the site using AWS cloud hosting for scalability and performance.
	\item Completed the course with an A+.}
\end{tightemize}

\begin{skillsection}
{\custombolder{Skills:} PHP \textbullet{} MySQL \textbullet{} JavaScript \textbullet{} HTML5 \textbullet{} CSS3 \textbullet{}AJAX \textbullet{} AWS \textbullet{} Docker \textbullet{} Figma \textbullet{} User Experience (UX)}
\end{skillsection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\end{minipage}
\end{document}
